---
title: "VPS4A/B analytics report"
author: "Guillaume Kugener"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include=FALSE, warning = FALSE, message = FALSE)

source('~/Documents/Projects/BroadInstitute/gkugener/RScripts/load_libraries_and_annotations.R')
```

```{r echo=TRUE, results='hide'}
plot_saving_directory <- '../plots/cn_in_tcga/'
dir.create(plot_saving_directory)
```

```{r eval=FALSE}
# To push this to CDS_Projects
cds_render(path_to_rmd = '~/Documents/Projects/BroadInstitute/VPS4A/analysis_scripts/cn_in_tcga.Rmd', folder = 'VPS4A', path_to_html = '~/Documents/Projects/BroadInstitute/VPS4A/html_reports/cn_in_tcga.html')
```

```{r echo=TRUE, results='hide'}
public.CCLE.expression <- load.from.taiga(data.name='public-19q2-5572', data.version=10, data.file='CCLE_expression')
public.CCLE.gene.cn <- load.from.taiga(data.name='public-19q2-5572', data.version=10, data.file='CCLE_gene_cn')
public.CCLE.gene.cn <- log2(2^public.CCLE.gene.cn-1)
```

```{r echo=TRUE, results='hide'}
# Load in the CN, ABSOLUTE
absolute <- load.from.taiga(data.name='tcga-copy-number-profiles-0f8f', data.version=1, data.file='TCGA_mastercalls.abs_tables_JSedit.fixed')
cn_profiles <- load.from.taiga(data.name='tcga-copy-number-profiles-0f8f', data.version=1, data.file='all_data_by_genes_whitelisted')
```

```{r echo=TRUE, results='hide'}
# Load lineage annotations
lineage_info_tcga <- load.from.taiga(data.name='tcga-copy-number-profiles-0f8f', data.version=1, data.file='TCGA-CDR-SupplementalTableS1')
```

```{r}
vps4a_b_only <- cn_profiles %>% 
  filter(`Gene Symbol` %in% c('VPS4A', 'VPS4B')) %>%
  gather(Sample, CN, -`Gene Symbol`, -`Locus ID`, -`Cytoband`) %>%
  mutate(Patient_ID=gsub('\\-[0-9A-Z]+\\-[0-9A-Z]+\\-([0-9A-Z])+\\-[0-9]+$','', Sample)) %>%
  filter(!is.na(CN))

# Add lineage info
vps4a_b_only %<>% 
  left_join(., lineage_info_tcga %>% dplyr::select(Patient_ID=bcr_patient_barcode, type), by='Patient_ID')

# Add ploidy
vps4a_b_only %<>% left_join(., absolute %>% dplyr::select(Sample=sample, purity, ploidy), by=c('Sample')) %>%
  mutate(`ABSOLUTE CN`=(2^CN) * ploidy) %>% mutate(type=ifelse(is.na(type), 'None listed', type))

# Type order -> by the median relative CN
# type_plot_order <- c((vps4a_b_only %$% unique(type) %>% .[. != 'None listed']), 'None listed')
type_plot_order_vps4b <- vps4a_b_only %>%
  group_by(type) %>%
  filter(`Gene Symbol`=='VPS4B') %>%
  dplyr::summarise(MED_CN=median(CN)) %>%
  arrange(MED_CN) %$%
  as.character(type)

type_plot_order_vps4a <- vps4a_b_only %>%
  group_by(type) %>%
  filter(`Gene Symbol`=='VPS4A') %>%
  dplyr::summarise(MED_CN=median(CN)) %>%
  arrange(MED_CN) %$%
  as.character(type)
```

## CN by cancer type

The plot below looks at relative log2 CN across the different lineages. The dashed lines mark the cutoffs for deep (< -0.7), shallow (-0.7 < CN < -0.2), and neutral (-0.2 < CN < 0.2) cutoffs.

```{r}
loss_thresholds <- data.frame(
  loss_type=c('deep', 'shallow', 'neutral'),
  cutoff=c(-0.7, -0.2, 0.2), stringsAsFactors = F
)

loss_thresholds_list <- loss_thresholds %$% setNames(cutoff, loss_type)
```

```{r}
# Need to determine whisker plot cutoffs
vps4a_b_only %>% 
  filter(`Gene Symbol`=='VPS4A') %>%
  group_by(type) %>%
  dplyr::summarise(
    yend=quantile(CN, c(.75))[1]
  ) %>%
  mutate(y=-0.7) %>%
  filter(yend < -0.7)
```

```{r fig.height=10, include=TRUE}
vps4a_b_only %<>% mutate(type=factor(type, levels=type_plot_order_vps4a))

p1_vps4a <- ggplot(vps4a_b_only %>% filter(`Gene Symbol`=='VPS4A'), 
                   aes(type, CN, alpha=CN < -0.7, color=CN < -0.7, fill=CN < -0.7)) +
  geom_point(position=position_jitter(width = 0.2), pch=21) +
  geom_boxplot(color='#807e7f', outlier.shape = NA, fill='grey', alpha=0.5) +
  scale_alpha_discrete(range=c(0.2, 1)) + 
  scale_fill_manual(values=c('grey', 'red')) +
  scale_color_manual(values=c('grey', 'black')) +
  geom_hline(data=loss_thresholds, aes(yintercept=cutoff), linetype=2) +
  ylab('Relative log2(CN)') + xlab('') +
  facet_wrap(~`Gene Symbol`, ncol = 1) +
  ggtitle('VPS4A relative CN across TCGA') +
  theme_Publication() + 
  scale_y_continuous(limits=c(-1.5, 1.5), breaks=pretty_breaks(n=10)) +
  theme(legend.position='none', axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))

p1_vps4a

ggsave(
  p1_vps4a, filename = file.path(plot_saving_directory, 'vps4a_relative_cn_across_types.pdf'), device = 'pdf',
  width = 12, height = 5
)
```

```{r fig.height=10, include=TRUE}
vps4a_b_only %<>% mutate(type=factor(type, levels=type_plot_order_vps4b))

p1_vps4b <- ggplot(vps4a_b_only %>% filter(`Gene Symbol`=='VPS4B'), 
                   aes(type, CN, alpha=CN < -0.7, color=CN < -0.7, fill=CN < -0.7)) +
  geom_point(position=position_jitter(width = 0.2), pch=21) +
  geom_boxplot(color='#807e7f', outlier.shape = NA, fill='grey', alpha=0.5) +
  scale_alpha_discrete(range=c(0.2, 1)) + 
  scale_fill_manual(values=c('grey', 'red')) +
  scale_color_manual(values=c('grey', 'black')) +
  geom_hline(data=loss_thresholds, aes(yintercept=cutoff), linetype=2) +
  ylab('Relative log2(CN)') + xlab('') +
  facet_wrap(~`Gene Symbol`, ncol = 1) +
  ggtitle('VPS4B relative CN across TCGA') +
  theme_Publication() + 
  scale_y_continuous(limits=c(-1.5, 1.5), breaks=pretty_breaks(n=10)) +
  theme(legend.position='none', axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))

p1_vps4b

# ggplotly(ggplot(vps4a_b_only %>% filter(`Gene Symbol`=='VPS4B'), aes(type, CN)) +
#  geom_boxplot())  

ggsave(
  # For plotting purposes, we want to make the box plot that goes below -0.7 darker
  p1_vps4b,
  filename = file.path(plot_saving_directory, 'vps4b_relative_cn_across_types.pdf'), device = 'pdf',
  width = 12, height = 5
)
```

```{r}
# For each sample, label the category of loss and then list the results
vps4a_b_only %<>% mutate(`Loss type`=ifelse(CN < loss_thresholds_list['deep'], 'deep', ifelse(
  CN < loss_thresholds_list['shallow'], 'shallow', ifelse(
    CN < loss_thresholds_list['neutral'], 'neutral', 'gain'
  )
)))
```

```{r eval=FALSE}
vps4a_b_only %>%
  filter(`Gene Symbol`=='VPS4B') %>%
  dplyr::rename(relative_cn=CN) %>%
  write.table(., file = '~/Documents/Projects/BroadInstitute/VPS4A/tcga_vps4b_copy_number.tsv', sep = '\t', quote = F, row.names = F)

vps4a_b_only %>%
  filter(`Gene Symbol`=='VPS4A') %>%
  dplyr::rename(relative_cn=CN) %>%
  write.table(., file = '~/Documents/Projects/BroadInstitute/VPS4A/tcga_vps4a_copy_number.tsv', sep = '\t', quote = F, row.names = F)


vps4a_b_only %>%
  group_by(`Gene Symbol`, type) %>%
  mutate(total=n()) %>%
  group_by(`Gene Symbol`, type, `Loss type`, total) %>%
  dplyr::summarise(count=n()) %>% mutate(fraction=count/total) %>%
  mutate_if(is.numeric, funs(round(.,3))) %>%
  dplyr::rename(`total samples in context`=total) %>%
  write.table(., file = '~/Documents/Projects/BroadInstitute/VPS4A/vps4ab_copy_number_by_cancer_type.tsv', sep = '\t', quote = F, row.names = F)
```

The table below outlines the numbers for types of CN events for VPS4A and VPS4B in the TCGA data.

```{r include=TRUE}
vps4a_b_only %>%
  group_by(`Gene Symbol`, type) %>%
  mutate(total=n()) %>%
  group_by(`Gene Symbol`, type, `Loss type`, total) %>%
  dplyr::summarise(count=n()) %>% mutate(fraction=count/total) %>%
  mutate_if(is.numeric, funs(round(.,3))) %>%
  dplyr::rename(`total samples in context`=total) %>%
  datatable(options=list(scrollX=T), filter='top')
```

The plot below is the same as above but this time using absolute CN (relative CN * ploidy from ABSOLUTE)

```{r fig.height=10, include=TRUE}
# Multiply the relative CN by ploidy and purity?
p2 <- ggplot(vps4a_b_only, aes(type, `ABSOLUTE CN`, fill=type, color=type)) +
  geom_point(position=position_jitterdodge()) +
  geom_boxplot(color='black', outlier.color = 'transparent') +
  ylab('Absolute CN (ploidy * relative CN)') + xlab('') +
  ggtitle('Absolute CN of VPS4A/B in TCGA') +
  facet_wrap(~`Gene Symbol`, ncol = 1) +
  scale_y_continuous(limits=c(0,5), breaks=pretty_breaks(n=10)) +
  theme_Publication() + 
  theme(legend.position='none', axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))

p2

ggsave(
  p2, filename = file.path(plot_saving_directory, 'absolute_cn_across_types.pdf'), device = 'pdf',
  width = 12, height = 10
)
```

## Combined VPS4A+B CN score

In the plot below, for each sample, we are calculating a combined VPS4A/B CN score (sum of the two relative CN), and then plotting by lineage. In this plot, because we are looking at CN of VPS4A + VPS4B and then taking the log2, we expect that 'normal' is around 1 (as 2^1=2).

```{r}
# Because it is log2, we can't just sum, we need to sum the non log2 data and then take the log2 of that
combined_vps4ab_cn_score <- vps4a_b_only %>% 
  group_by(Sample, Patient_ID, type, purity, ploidy) %>%
  dplyr::summarise(Combined_CN=log2(sum((2^CN))))

combined_vps4ab_cn_type_order <- combined_vps4ab_cn_score %>%
  group_by(type) %>%
  dplyr::summarise(med_CN=median(Combined_CN)) %>%
  arrange(med_CN) %$% as.character(type)
```

```{r include=TRUE}
p3 <- ggplot(combined_vps4ab_cn_score %>% 
         ungroup() %>%
         mutate(type=factor(type, levels=combined_vps4ab_cn_type_order)), 
       aes(type, Combined_CN, fill=type, color=type)) +
  geom_point(position=position_jitterdodge()) +
  geom_boxplot(color='black', outlier.color = 'transparent') +
  # geom_hline(data=loss_thresholds, aes(yintercept=cutoff), linetype=2) +
  ylab('Relative CN') + xlab('') +    
  # scale_y_continuous(limits=c(-2,3), breaks=pretty_breaks(n=10)) +
  ggtitle('VPS4A+B relative CN in TCGA') +
  theme_Publication() + 
  theme(legend.position='none', axis.text.x = element_text(angle=90, hjust=1, vjust=0.5))

p3

ggsave(
  p3, filename = file.path(plot_saving_directory, 'relative_combined_cn_across_types.pdf'), device = 'pdf',
  width = 12, height = 10
)
```

## Combined VPS4A/B expression/CN with dependency data

Given how related VPS4A/B are, we are interested in seeing if combining the expression/CN of these two genes to generate one VPS4 expression/CN score is more strongly associated with VPS4A/B dependency and if potentially other interested targets fall out in dependency space.

### Expression

To start and to keep things simple, we will create a total VPS4 expression score by summing the expression of VPS4A/B in depmap data. We will call this new score VPS4A_B in the plots below.

```{r}
# Create new VPS4A_B gene
vps4_expression <- public.CCLE.expression[,c("VPS4A (27183)", "VPS4B (9525)")] %>% 
  as.data.frame() %>% 
  mutate(DepMap_ID=row.names(.)) %>%
  mutate(VPS4A_B=log2(2^get("VPS4A (27183)") + 2^get("VPS4B (9525)"))) %>%
  set_rownames(.$DepMap_ID)
```

```{r}
# Differences by lineage
mf <- pull_mf(version=203)
by_lineage_expressions <- vps4_expression %>%
  left_join(., mf %>% dplyr::select(DepMap_ID, Type), by='DepMap_ID') %>%
  gather(Gene, Expression, -DepMap_ID, -Type) %>%
  mutate(Gene=factor(Gene, levels=c('VPS4A (27183)', 'VPS4B (9525)', 'VPS4A_B')))

```


```{r include=TRUE, fig.height=15}
p5 <- ggplot(by_lineage_expressions, aes(Type, Expression, fill=Type)) +
  geom_boxplot(outlier.color = 'transparent') +
  facet_wrap(~Gene, ncol=1) +
  coord_flip() +
  ggtitle('VPS4A, VPS4B, and VPS4A+B expression in TCGA') +
  theme_Publication() +
  theme(
    axis.text.x = element_text(angle=90, hjust=1, vjust=0.5),
    legend.position = 'none'
  )

p5

ggsave(
  p5, filename = file.path(plot_saving_directory, 'combined_expression_vps4ab_dm.pdf'), device = 'pdf',
  width = 6, height = 15
)
```

### CN

To start and to keep things simple, we will create a total VPS4 expression score by summing the expression of VPS4A/B in depmap data. We will call this new score VPS4A_B in the plots below

```{r}
# Create new VPS4A_B gene
vps4_cn <- public.CCLE.gene.cn[,c("VPS4A (27183)", "VPS4B (9525)")] %>% 
  as.data.frame() %>% 
  mutate(DepMap_ID=row.names(.)) %>%
  mutate(VPS4A_B=log2(2^get("VPS4A (27183)") + 2^get("VPS4B (9525)"))) %>%
  set_rownames(.$DepMap_ID)
```

```{r}
# Differences by lineage
by_lineage_cn <- vps4_cn %>%
  left_join(., mf %>% dplyr::select(DepMap_ID, Type), by='DepMap_ID') %>%
  gather(Gene, CN, -DepMap_ID, -Type) %>%
  mutate(Gene=factor(Gene, levels=c('VPS4A (27183)', 'VPS4B (9525)', 'VPS4A_B')))
```

```{r include=TRUE, fig.height=15}
p7 <- ggplot(by_lineage_cn, aes(Type, CN, fill=Type)) +
  geom_boxplot(outlier.color = 'transparent') +
  facet_wrap(~Gene, ncol=1) +
  coord_flip() +
  ylab('log2(relative CN)') + xlab('') +
  ggtitle('VPS4A, VPS4B, and VPS4A+B CN in TCGA') +
  theme_Publication() +
  theme(
    axis.text.x = element_text(angle=90, hjust=1, vjust=0.5),
    legend.position = 'none'
  )

p7

ggsave(p7, filename = file.path(plot_saving_directory, 'combined_cn_vps4ab_dm.pdf'), device = 'pdf',
  width = 6, height = 6)
```

## RNA and CN correlation in TCGA

We generated a similar plots in CCLE. We are interested to see where the relationship between VPS4A/B expression and copy number falls in relation to other genes in TCGA. In the plots below, we plot the correlation of expression and relative copy number of a set of 4000 randomly selected genes and VPS4A and VPS4B. There are also individual plots for VPS4A/B expression and CN in the cohort.

```{r}
# Load the TCGA expression data we have
tcga.expression.data <- load.from.taiga(data.name='rnaseq-7cdc', data.version=1, data.file='expression_tpm')
change_row_names <- row.names(tcga.expression.data) %>% stringr::str_extract(pattern='ENSGR?[0-9]+', string=.)
row.names(tcga.expression.data) <- change_row_names
```


```{r}
# We only want coding genes for this analysis
hg29_ids <- read_csv('~/Documents/Projects/BroadInstitute/gkugener/RScripts/Common_annotations/v29_ensembl_hgnc_gene_names.csv') %>%
  filter(ensembl_gene_id %in% stringr::str_extract(pattern='ENSG[0-9]+', string=row.names(tcga.expression.data))) %$%
  setNames(hgnc_id, ensembl_gene_id)

tcga.expression.data <- tcga.expression.data[intersect(row.names(tcga.expression.data), names(hg29_ids)),]
row.names(tcga.expression.data) %<>% hg29_ids[.]

tcga.expression.data %<>% t()

# Convert to log2 + 1
tcga.expression.data <- log2(2^tcga.expression.data + 1)
```

```{r}
# Generate cn matrix of TCGA copy number
cn_profile_matrix <- cn_profiles %>%
  filter(`Gene Symbol` %in% colnames(tcga.expression.data)) %>%
  dplyr::select(-`Locus ID`, -Cytoband) %>%
  set_colnames(gsub('[A-Z]\\-[A-Z0-9]+\\-[A-Z0-9]+\\-[0-9]+$', '', colnames(.))) %>%
  column_to_rownames(var='Gene Symbol') %>%
  t()
```

```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
# you need to have installed "pkg-config cairo libpng jpeg giflib" with brew or apt..
BiocManager::install(c("GO.db","impute","preprocessCore", "latticeExtra"))
install.packages('WGCNA',)
```
```{rzz}
library(WGCNA)
```
```{r}
install.packages("impute", "preprocessCore", "GO.db")
```

```{r}
overlapping_tcga_cn_tpm <- intersect(row.names(cn_profile_matrix), row.names(tcga.expression.data))
common_genes_between_tcga_datatsets <- intersect(colnames(cn_profile_matrix), colnames(tcga.expression.data))

# Randomly sample 4000 genes from each dataset (including VPS4A and VPS4B in both)
tcga_genes_chosen <- sample(common_genes_between_tcga_datatsets, size=300)
tcga_genes_chosen <- c(common_genes_between_tcga_datatsets, c("VPS4A", "VPS4B")) %>% unique()

# Think about removing non-expressed genes?
correlations_matrix_cn_rnaseq_tcga <- WGCNA::cor(
  cn_profile_matrix[overlapping_tcga_cn_tpm,tcga_genes_chosen],
  tcga.expression.data[overlapping_tcga_cn_tpm,tcga_genes_chosen],
  # use = 'pairwise.complete', 
  method = 'pearson'
)

# Look at the distributions (may also want to look at this paralog correlation business)
correlations_tcga_annotated <- NULL
for (i in seq(1,ncol(correlations_matrix_cn_rnaseq_tcga), 2500)) {
  print(i)
  end <- min(i + 2500, ncol(correlations_matrix_cn_rnaseq_tcga))
  correlations_tcga_annotated_p <- correlations_matrix_cn_rnaseq_tcga[,i:end] %>%
    as.data.frame() %>%
    mutate(CN_gene=row.names(.)) %>%
    gather(Expression_gene, correlation, -CN_gene)
  
  if (is.null(correlations_tcga_annotated)) {
    correlations_tcga_annotated <- correlations_tcga_annotated_p
  } else {
    correlations_tcga_annotated %<>% rbind(., correlations_tcga_annotated_p)
  }
}

# correlations_dm_annotated %<>% left_join(., paralogs, by=c('CN_gene', 'Expression_gene'))
correlations_tcga_annotated %<>% mutate(type=factor(case_when(
#   CN_gene==Expression_gene ~ 'same_gene',
#   source=='paralog' ~ 'paralogs',
#   TRUE ~ 'unrelated'
# ), levels=c('unrelated', 'paralogs', 'same_gene'))) %>%
#   mutate(type=factor(case_when(
  CN_gene==Expression_gene ~ 'same gene',
  # source=='paralog' ~ 'paralogs',
  TRUE ~ 'different gene'
), levels=c('different gene', 'same gene')))
```

```{r include=TRUE}
tcga_vps4ab_annotations_density_plot <- correlations_tcga_annotated %>%
  filter(type != 'different gene') %>%
  filter(Expression_gene==CN_gene, grepl('VPS4[AB]', CN_gene) | grepl('VPS4[AB]', Expression_gene))

# Label VPS4A/B on the plot 
tcga_expression_cn_correlation_plots_vps4ab <- ggplot(correlations_tcga_annotated, aes(correlation, fill=type)) +
  geom_density(alpha=0.5) +
  geom_point(data=tcga_vps4ab_annotations_density_plot, aes(y=0), show.legend = F) +
  geom_label_repel(data=tcga_vps4ab_annotations_density_plot,
    aes(y=0, label=paste0(gsub(' .*', '', Expression_gene), ' (Expression) \nand ', gsub(' .*', '', CN_gene), ' (CN)')),
    fill=rgb(1,1,1,0.5), force=10, size=10*1/ggplot2:::.pt,
    arrow = arrow(length = unit(0.03, "npc"))
  ) +
  ggtitle('Expression and copy number correlation in TCGA') +
  xlab('Pearson correlation') +
  guides(fill=guide_legend(title = 'Correlation pair')) +
  scale_fill_Publication() +
  theme_Publication() +
  theme(
    text = element_text(size=10),
    title = element_text(size=16),
    axis.text = element_text(size = 16),
    legend.position = c(1,1),
    legend.justification = c(1,1)
  )

tcga_expression_cn_correlation_plots_vps4ab

ggsave(tcga_expression_cn_correlation_plots_vps4ab, filename = file.path(plot_saving_directory, 'tcga_expr_cn_correlations.pdf'), width=6, height=6)
```

```{r}
# Individual plots for VPS4B and VPS4A
tcga_vps4_plots <- inner_join(
  cn_profile_matrix[,c("VPS4A", "VPS4B")] %>%
    as.data.frame() %>%
    mutate(sample=row.names(.)) %>%
    gather(gene, CN, -sample),
  tcga.expression.data[overlapping_tcga_cn_tpm,c("VPS4A", "VPS4B")] %>%
    as.data.frame() %>%
    mutate(sample=row.names(.)) %>%
    gather(gene, expression, -sample),
  by=c('sample', 'gene'))
```

```{r include=TRUE}
vps4a_tcga_expr_cn <- tcga_vps4_plots %>% filter(gene=='VPS4A')

vps4a_tcga_expr_cn_plot <- ggplot(vps4a_tcga_expr_cn, aes(CN, expression)) +
  geom_point(alpha=0.25) +
  geom_smooth(method='lm', se=F) +
  ggtitle('VPS4A in TCGA') +
  xlab('VPS4A copy number (log2 relative to ploidy)') +
  ylab('VPS4A expression (log2(TPM+1))') +
  ylim(c(min(vps4a_tcga_expr_cn$expression, na.rm = T)-0.05, max(vps4a_tcga_expr_cn$expression, na.rm = T)+0.05)) + 
  xlim(c(min(vps4a_tcga_expr_cn$CN, na.rm = T)-0.05, max(vps4a_tcga_expr_cn$CN, na.rm = T)+0.05)) + 
  theme_Publication() +
  theme(
    title = element_text(size=16),
    text = element_text(size=10),
    axis.text = element_text(size=16)
  )

vps4a_tcga_expr_cn_plot

ggsave(vps4a_tcga_expr_cn_plot, filename = file.path(plot_saving_directory, 'VPS4A_expr_v_VPS4A_cn.pdf'), width = 5, height = 5.5)
```

```{r include=TRUE}
vps4b_tcga_expr_cn <- tcga_vps4_plots %>% filter(gene=='VPS4B')

vps4b_tcga_expr_cn_plot <- ggplot(vps4b_tcga_expr_cn, aes(CN, expression)) +
  geom_point(alpha=0.25) +
  geom_smooth(method='lm', se=F) +
  ggtitle('VPS4B in TCGA') +
  xlab('VPS4B copy number (log2 relative to ploidy)') +
  ylab('VPS4B expression (log2(TPM+1))') +
  ylim(c(min(vps4b_tcga_expr_cn$expression, na.rm = T)-0.05, max(vps4b_tcga_expr_cn$expression, na.rm = T)+0.05)) + 
  xlim(c(min(vps4b_tcga_expr_cn$CN, na.rm = T)-0.05, max(vps4b_tcga_expr_cn$CN, na.rm = T)+0.05)) + 
  theme_Publication() +
  theme(
    title = element_text(size=16),
    text = element_text(size=10),
    axis.text = element_text(size=16)
  )

vps4b_tcga_expr_cn_plot

ggsave(vps4b_tcga_expr_cn_plot, filename = file.path(plot_saving_directory, 'VPS4B_expr_v_VPS4B_cn.pdf'), width = 5, height = 5.5)
```







