---
title: "Assess SOLID RMS CN"
author: "Guillaume Kugener"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include=FALSE, message = FALSE, warning = FALSE)
source('~/Documents/gkugener/RScripts/load_libraries_and_annotations.R')
```

```{r echo=FALSE, results='hide'}
rms.wes.annotations <- load.from.taiga(data.name='rms-nih-936f', data.version=7, data.file='rms_wes_annotations')

solid.wes.normal.gene.level.cn <- load.from.taiga(data.name='rms-nih-936f', data.version=7, data.file='solid_wes_normal_gene_level_cn')
solid.wes.normal.segmented.cn <- load.from.taiga(data.name='rms-nih-936f', data.version=7, data.file='solid_wes_normal_segmented_cn')
solid.wes.tumor.gene.level.cn <- load.from.taiga(data.name='rms-nih-936f', data.version=7, data.file='solid_wes_tumor_gene_level_cn')
solid.wes.tumor.segmented.cn <- load.from.taiga(data.name='rms-nih-936f', data.version=7, data.file='solid_wes_tumor_segmented_cn')

cyto_band_file <- '~/Documents/Analysis/RScripts/Common_annotations/hg19_cytoBand.txt.gz'

plot_saving_directory <- '~/Documents/gkugener/VPS4A/plots/qc_solid/'
dir.create(plot_saving_directory)
```

```{r}
all_samples_solid <- rbind(
  solid.wes.normal.segmented.cn,
  solid.wes.tumor.segmented.cn
) %>% left_join(., rms.wes.annotations %>% dplyr::select(Sample=Run, Subject_ID, Histological_Type, Tumor_Sample=Tumor), by='Sample')

gene_level_calls_vps4ab <- solid.wes.tumor.gene.level.cn[,c("VPS4A (27183)", "VPS4B (9525)")] %>%
  as.data.frame() %>%
  mutate(Run=row.names(.)) %>%
  left_join(., rms.wes.annotations %>% dplyr::select(Run, Histological_Type), by='Run') %>%
  gather(SYMBOL, CN, -Run, -Histological_Type)
```

```{r}
# Have to edit the chr values to 
chr_bp_cutoffs <- read_tsv(cyto_band_file, col_names = F)
cutoffs <- chr_bp_cutoffs %>% 
  group_by(X1) %>% 
  dplyr::summarize(pos=max(X3)) %>%
  mutate(X1=gsub('chr', '', X1)) %$% 
  setNames(pos, ifelse(X1 %in% seq(1,21), paste0('chr', as.integer(X1) + 1), ifelse(X1==22, 'chrX', ifelse(X1=='X', 'chrY', 'chrZ'))))

cutoffs_final <- cutoffs[paste0('chr',c(seq(2, 22), 'X', 'Y'))] %>% cumsum()
cutoffs_final['chr1'] = 0

cutoffs_chr_for_plotting <- cutoffs_final
```

```{r}
chr_order <- paste0('chr', c(seq(1,22), 'X', 'Y'))
sample_order <- rms.wes.annotations %>% 
  dplyr::select(sample=Run, Histological_Type) %>% 
  distinct() %>%
  filter(sample %in% solid.wes.tumor.segmented.cn$Sample) %>%
  arrange(Histological_Type) %$% 
  sample

plot_ready_cn <- all_samples_solid %>% filter(Sample %in% solid.wes.tumor.segmented.cn$Sample) %>%
  mutate(sample=factor(Sample, level=sample_order)) %>%
  # mutate(Chromosome=factor(Chromosome, levels=chr_order)) %>%
  mutate(Segment_Mean=ifelse(log2(Segment_Mean) < -1, -1, ifelse(log2(Segment_Mean) > 1, 1, log2(Segment_Mean)))) %>%
  mutate(Start_new=Start + cutoffs_final[paste0('chr', Chromosome)], End_new=End+cutoffs_final[paste0('chr', Chromosome)])

cutoffs_chr_for_plotting['chr1'] = min(plot_ready_cn$Start_new)
```

```{r}
labels_cn_plots <- plot_ready_cn %>%
  mutate(HT=stringr::str_extract(string=Histological_Type, pattern='^[A-Z]')) %>%
  mutate(HT=gsub('R', 'N', HT)) %>%
  # mutate(Histological_Type=gsub('Mixed Alveolar/Embryonal', 'Mixed', Histological_Type)) %>% 
  group_by(HT, Histological_Type) %>%
  dplyr::summarise(m=mean(as.integer(sample))) %>% 
  mutate(y=(-10^8)/2)
```

In the plot below, the annotations at the top correspond to the following:

* A: ARMS
* E: ERMS
* M: Mixed histology
* N: RMS - Not specificed

```{r fig.height=10, include=TRUE}
general_plot_overview <- ggplot(plot_ready_cn, aes(xmin=as.integer(sample)-1, xmax=as.integer(sample), ymin=Start_new, ymax=End_new, fill=Segment_Mean)) +
  geom_rect() +
  geom_rect(data=plot_ready_cn %>% 
              filter(grepl('Alveolar', Histological_Type)) %>% 
              distinct(sample) %>% mutate(Start_new=-10^8, End_new=0), 
            fill=cols_to_use_for_groups[1]) +
  geom_rect(data=plot_ready_cn %>% 
              filter(grepl('Embryonal', Histological_Type)) %>%
              distinct(sample, Histological_Type) %>% 
              mutate(Start_new=-10^8, End_new=0), 
            fill=cols_to_use_for_groups[2]) +
  geom_rect(data=plot_ready_cn %>% 
                filter(grepl('NOS', Histological_Type)) %>% 
                distinct(sample, Histological_Type) %>%
                mutate(Start_new=-10^8, End_new=0), 
              fill=cols_to_use_for_groups[3]) +
  geom_rect(data=plot_ready_cn %>% 
              filter(grepl('Mixed', Histological_Type)) %>%
              distinct(sample, Histological_Type) %>%
              mutate(Start_new=-10^8, End_new=0), 
            fill=cols_to_use_for_groups[4]) +
  geom_text(data=labels_cn_plots %>% mutate(Segment_Mean=1), aes(x=m, y=y, xmin=m, xmax=m, ymin=y, ymax=y, label=HT)) +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(
    breaks=cutoffs_chr_for_plotting[paste0('chr', seq(1,22,1))],
    labels=names(cutoffs_chr_for_plotting[paste0('chr', seq(1,22,1))]),
    expand = c(0,0), trans = 'reverse') +
  scale_fill_gradient2(high='red', low='blue', mid='white', midpoint=0, 
    guide = guide_colorbar(frame.colour = "black", ticks.colour = "black", title.position = "left",
      title.hjust = 0.5, title.vjust = 0.5, title.theme = element_text(angle = 90), title = 'log2 relative CN')
  ) + 
  xlab('Sample') +
  # theme_minimal() +
  theme(
    text = element_text(size=12),
    axis.title = element_blank(),
  #   # axis.text.y = element_text(color = colors_by_cell_line[names(integer_values_ccle_name)]),
    # axis.text.y = element_blank(),
    # axis.ticks.y = element_blank(),
    # axis.text.x=element_text(hjust = 1, angle=90, vjust=0.5),
    # axis.text.x = element_blank(),
    # axis.ticks.x = element_blank(),
    panel.grid = element_blank(),
    # plot.background = element_rect(color='black', fill='transparent'),
    # plot.margin=unit(c(.2,0,.1,1),"cm"),
    legend.position = 'left'
  )

general_plot_overview
```

```{r}
ggsave(general_plot_overview, filename = file.path(plot_saving_directory, 'cn_all_chromosomes.pdf'), device = 'pdf', width = 15, height = 20, units = 'cm')
```

```{r, include=TRUE}
chr18_only_general_plot_overview <- ggplot(plot_ready_cn %>% filter(Chromosome=='18'), aes(xmin=as.integer(sample)-1, xmax=as.integer(sample), ymin=Start, ymax=End, fill=Segment_Mean)) +
  geom_rect() +
  geom_rect(data=plot_ready_cn %>% 
              filter(grepl('Alveolar', Histological_Type)) %>% 
              distinct(sample) %>% mutate(Start=-10^7, End=0), 
            fill=cols_to_use_for_groups[1]) +
  geom_rect(data=plot_ready_cn %>% 
              filter(grepl('Embryonal', Histological_Type)) %>%
              distinct(sample, Histological_Type) %>% 
              mutate(Start=-10^7, End=0), 
            fill=cols_to_use_for_groups[2]) +
  geom_rect(data=plot_ready_cn %>% 
                filter(grepl('NOS', Histological_Type)) %>% 
                distinct(sample, Histological_Type) %>%
                mutate(Start=-10^7, End=0), 
              fill=cols_to_use_for_groups[3]) +
  geom_rect(data=plot_ready_cn %>% 
              filter(grepl('Mixed', Histological_Type)) %>%
              distinct(sample, Histological_Type) %>%
              mutate(Start=-10^7, End=0), 
            fill=cols_to_use_for_groups[4]) +
  geom_text(data=labels_cn_plots %>% mutate(Segment_Mean=1), aes(x=m, y=(-10^7)/2, xmin=m, xmax=m, ymin=0, ymax=0, label=HT)) +
  xlab('samples') + ylab('position on chr18') + 
  scale_x_continuous(expand=c(0,0)) +
  scale_y_continuous(expand=c(0,0), trans = 'reverse') +
  scale_fill_gradient2(high='red', low='blue', mid='white', midpoint=0, 
    guide = guide_colorbar(frame.colour = "black", ticks.colour = "black", title.position = "left",
      title.hjust = 0.5, title.vjust = 0.5, title.theme = element_text(angle = 90), title = 'log2 relative CN')
  ) +
  geom_hline(yintercept = 61056423, linetype=2) +
  theme(
    text = element_text(size=12),
    # axis.title = element_blank(),
  #   # axis.text.y = element_text(color = colors_by_cell_line[names(integer_values_ccle_name)]),
    # axis.text.y = element_blank(),
    # axis.ticks.y = element_blank(),
    # axis.text.x=element_text(hjust = 1, angle=90, vjust=0.5),
    # axis.text.x = element_blank(),
    # axis.ticks.x = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(color='black', fill='grey'),
    # plot.margin=unit(c(.2,0,.1,1),"cm"),
    legend.position = 'left'
  )

chr18_only_general_plot_overview
```

```{r}
# chr18 plots only
ggsave(chr18_only_general_plot_overview, filename = file.path(plot_saving_directory, 'chr18_only.pdf'), device = 'pdf', units = 'cm', width = 16, height = 12)
```

```{r, include=TRUE}
ggplot(gene_level_calls_vps4ab, aes(Histological_Type, CN)) +
  geom_boxplot() +
  geom_point(position=position_jitter()) +
  facet_wrap(~SYMBOL) +
  ylab('log2(relative CN+1)') +
  theme(
    axis.text.x = element_text(angle=90, hjust=1, vjust=0.5)
  )
```


```{r}
vps4ab_plot <- gene_level_calls_vps4ab %>%
  # This sample looks like a fail
  filter(Run != 'SRR1591854') %>%
  filter(grepl('VPS4[AB]', SYMBOL)) %>%
  arrange(CN) %>%
  dcast(Run + Histological_Type ~ SYMBOL, value.var='CN') %>%
  arrange(`VPS4B (9525)`) %>%
  set_colnames(gsub(' \\([0-9]+\\)', '', colnames(.)))
```

```{r, include=TRUE}
vps4_a_b <- ggplot(vps4ab_plot, aes(VPS4A, VPS4B, color=Histological_Type)) +
  geom_hline(yintercept = log2(2^-0.3+1), linetype=2) +
  geom_hline(yintercept = log2(2^-0.6+1), linetype=2) +
  geom_point() +
  xlab('log2(relative VPS4A CN)') + ylab('log2(relative VPS4B CN)') +
  # geom_point(position=position_jitterdodge()) +
  # facet_wrap(~SYMBOL) +
  ylim(0, 2) + xlim(0, 2) +
  theme_Publication() +
  theme(legend.position = c(0.01, 1), legend.justification = c(0.01, 1))

vps4_a_b
```


```{r}
ggsave(vps4_a_b, filename = file.path(plot_saving_directory, 'vps4ab_cn_plot.pdf'), device = 'pdf', units = 'cm', width = 16, height = 16)
```

```{r}
# Filter for segments with probes above a threshold and then scale gain/loss to that threshold
passing_quality_patients <- all_samples_solid %>% 
  filter(Tumor_Sample=='no') %>% 
  filter(log2(Segment_Mean) < -1) %>% 
  group_by(Subject_ID) %>%
  dplyr::summarise(count=n()) %>% 
  arrange(-count) %>% 
  filter(count < 200) %$% 
  Subject_ID
```

We use the following plot to look at the relationship between number of probes and called copy number for segments. Samples that have many large segments (many probes) with low copy number are likely too noisy to use with confidence.

```{r, include=TRUE}
# Based on the plot below, we should filter out segments with probes below 10
ggplot(all_samples_solid %>% filter(Tumor_Sample=='no', Subject_ID %in% passing_quality_patients), aes((Num_Probes), log2(Segment_Mean))) +
  geom_point(alpha=0.1) +
  ggtitle('log2(CN) vs. number of probes in normal samples') +
  scale_x_continuous(trans = 'log10') +
  geom_vline(xintercept = 10, linetype=2)
```

```{r, include=TRUE}
# For 
ggplot(all_samples_solid %>% filter(Tumor_Sample=='yes', Subject_ID %in% passing_quality_patients), aes((Num_Probes), log2(Segment_Mean))) +
  geom_point(alpha=0.1) +
  ggtitle('log2(CN) vs. number of probes in tumor samples') +
  scale_x_continuous(trans = 'log10') +
  geom_vline(xintercept = 50, linetype=2)
```

```{r}
annotated_gene_level_matrix <- solid.wes.tumor.gene.level.cn %>%
  as.data.frame() %>%
  mutate(Sample=row.names(.)) %>%
  gather(SYMBOL, CN, -Sample) %>%
  left_join(., rms.wes.annotations %>% dplyr::select(Sample=Run, Tumor, Subject_ID, Histological_Type), by='Sample')

subject_id_order <- annotated_gene_level_matrix %>% 
  distinct(Subject_ID, Histological_Type) %>% 
  filter(Histological_Type != 'Blood') %>% 
  arrange(Histological_Type) %$% Subject_ID

# Add VPS4B to these samples below to see where it would fall
calling_attempt_plot <- annotated_gene_level_matrix %>% 
  filter(Subject_ID %in% passing_quality_patients) %>%
  filter(CN > log2(2^-5+1), abs((CN)) < log2(2^2+1)) %>% 
  # filter(Subject_ID %in% subject_id_order[21:40]) %>%
  mutate(Subject_ID=factor(Subject_ID, levels=subject_id_order)) %>%
  mutate(Tumor_name=ifelse(Tumor=='yes', 'Tumor', 'Normal'))

vps_4b_annotated_position <- calling_attempt_plot %>%
  filter(Tumor=='yes') %>%
  filter(grepl('VPS4B', SYMBOL))

full_plot_superimposed_vps4b <- ggplot(calling_attempt_plot, 
       aes((CN), Subject_ID, fill=Histological_Type)) +
  ggridges::geom_density_ridges(alpha=0.5) +
  geom_point(data=vps_4b_annotated_position, aes((CN), Subject_ID, label=gsub(' .*', '', SYMBOL)), color='orange',show.legend = F) +
  geom_text_repel(data=vps_4b_annotated_position, aes((CN), Subject_ID, label=gsub(' .*', '', SYMBOL)), color='black') +
  xlab('log2(relative CN + 1)') +
  facet_wrap(~Tumor_name) + 
  xlim(c(0, 2))

ggsave(full_plot_superimposed_vps4b, filename = file.path(plot_saving_directory, 'solid_gene_density_with_vps4b_label.pdf'), width = 24, height=60, units = 'cm')
```

Below, we plot the distribution of the gene level copy number in all of the SOLID tumor samples, highlighting where VPS4B appears for each sample.

```{r, include=TRUE, fig.height=10}
full_plot_superimposed_vps4b
```

```{r, eval=FALSE}
wes.priority.cn.gene.matrix <- load.from.taiga(data.name='segmented-cn-wes-prioritzed-7fe1', data.version=21, data.file='wes_priority_cn_gene_matrix')

subset_ccle_wes <- wes.priority.cn.gene.matrix[1:12,] %>%
  as.data.frame() %>%
  mutate(DM=row.names(.)) %>%
  gather(gene, cn, -DM)
```

```{r, include=TRUE, eval=FALSE}
ggplot(subset_ccle_wes, aes(log2(cn), DM)) +
  ggridges::geom_density_ridges() + 
  xlim(c(-1, 1))
```

```{r}
# WES_RMS_1003449 chromosome 10 looks like it was missed?
# arrange by type, median MEAN_LOG2_COPY_RATIO in type
data_for_plot_rms_scaling <- all_samples_solid %>%
  filter(Tumor_Sample=='yes', Subject_ID %in% passing_quality_patients, Subject_ID != '1003449', Num_Probes > 100)

sample_order_scaling_plot <- data_for_plot_rms_scaling %>%
  group_by(Subject_ID) %>%
  dplyr::summarise(m=median(log2(Segment_Mean))) %>%
  ungroup() %>%
  left_join(., 
    rms.wes.annotations %>%
      filter(Tumor=='yes') %>% 
      dplyr::select(Subject_ID, Histological_Type) %>% 
      distinct(), by='Subject_ID') %>%
  arrange(Histological_Type, m) %$% Subject_ID

data_for_plot_rms_scaling %<>% 
   mutate(patient_id=factor(Subject_ID, levels=sample_order_scaling_plot))

# Add VPS4AB data so we can see where it falls for each sample
vps4ab_cn_data_for_plot <- solid.wes.tumor.gene.level.cn[,c("VPS4A (27183)", "VPS4B (9525)")] %>%
  as.data.frame() %>%
  mutate(Sample=row.names(.)) %>%
  gather(SYMBOL, CN, -Sample) %>%
  left_join(., rms.wes.annotations %>% dplyr::select(Sample=Run, Tumor, Subject_ID, Histological_Type), by='Sample') %>%
  filter(Subject_ID %in% data_for_plot_rms_scaling$Subject_ID) %>%
  mutate(Subject_ID=factor(Subject_ID, levels=sample_order_scaling_plot)) %>%
  mutate(MEAN_LOG2_COPY_RATIO=(CN))
```

```{r, include=TRUE}
# Gene level
ggplot(data_for_plot_rms_scaling %>% filter(Histological_Type=='Alveolar'), aes(log2(Segment_Mean), patient_id, fill=Histological_Type)) +
  # geom_boxplot() +
  ggridges::geom_density_ridges() +
  # geom_point(data=vps4ab_cn_data_for_plot %>% filter(SYMBOL=='VPS4B'), color='red') +
  # geom_point(data=vps4ab_cn_data_for_plot %>% filter(SYMBOL=='VPS4A'), color='blue') +
  # ggtitle('log2(CN) vs. number of probes in normal samples') +
  theme_Publication() +
  theme(
    legend.position = 'bottom',
    # axis.text.x = element_blank()
  )
```
